---
title: Basic models
output: html_notebook
---

_Copyright (c) Microsoft Corporation._<br/>
_Licensed under the MIT License._

```{r, echo=FALSE, results="hide", message=FALSE}
library(tidyr)
library(dplyr)
library(tsibble)
library(feasts)
library(fable)
```

We fit some simple models to the orange juice data for illustrative purposes. Here, each model is actually a _group_ of models, one for each combination of store and brand. This is the standard approach taken in statistical forecasting, and is supported out-of-the-box by the tidyverts framework.

- `mean`: This is just a simple mean.
- `naive`: A random walk model without any other components. This amounts to setting all forecast values to the last observed value.
- `drift`: This adjusts the `naive` model to incorporate a straight-line trend.
- `arima`: An ARIMA model with the parameter values estimated from the data.

Note that the model training process is embarrassingly parallel on 3 levels:

- We have multiple independent training datasets;
- For which we fit multiple independent models;
- Within which we have independent sub-models for each store and brand.

This lets us speed up the training significantly. While the `fable::model` function can fit multiple models in parallel, we will run it sequentially here and instead parallelise by dataset. This avoids contention for cores, and also results in the simplest code.

```{r}
srcdir <- here::here("R_utils")
for(src in dir(srcdir, full.names=TRUE)) source(src)

load_objects("oj_retail", "data.Rdata")

cl <- make_cluster(libs=c("tidyr", "dplyr", "fable", "tsibble", "feasts"))

oj_modelset_basic <- parallel::parLapply(cl, oj_train, function(df)
{
    model(df,
        mean=MEAN(logmove),
        naive=NAIVE(logmove),
        drift=RW(logmove ~ drift()),
        arima=ARIMA(logmove ~ pdq() + PDQ(0, 0, 0)),
        .safely=FALSE
    )
})
oj_fcast_basic <- parallel::clusterMap(cl, get_forecasts, oj_modelset_basic, oj_test)

save_objects(oj_modelset_basic, oj_fcast_basic,
             example="oj_retail", file="model_basic.Rdata")

destroy_cluster(cl)

do.call(rbind, oj_fcast_basic) %>%
    mutate_at(-(1:3), exp) %>%
    eval_forecasts()
```

We can see that the ARIMA model does the best of the simple models, but not any better than a simple mean.

